
My field of research is focused in general on multivariate data analysis, and more specifically biplots and graphical visualisation of multi-dimensional data. My research is both on theoretical developments of methods for visualisation of multi-dimensional data, R software developed to implement methods and applications leading to new extensions of current methodology.
 
After a 13-year stint in the corporate world, I moved to academia in July 2009 as associate professor at the University of Cape Town and in January 2017, I joined Stellenbosch University as professor in statistics. I am an elected member of the International Statistics Institute, served on the executive committees of the International Federation of Classification Societies and the International Association of Statistical Computing. I am also the chair of the Multivariate Data Analysis Special Interest Group in the South African Statistical Association.
 
In July 2011 we formalised our research group into the Centre for Multi-dimensional Data Visualisation (MuViSU) located in the Department of Statistics and Actuarial Science at Stellenbosch University. As director of MuViSU I am proud to say we have a network of national and international members as well as post graduate students working on a variety of collaborative research projects.

---


# BOOKS

```{r}
#| echo: false
#| message: false
library(readr)
library(dplyr)
library(tidyr)
library(gt)
library(glue)
library(lubridate)
pubs <- read_csv("books.csv")
pubs |>
  mutate(titlelink = ifelse(is.na(Webpage), Title, glue("[{Title}]({Webpage})"))) |>
  arrange(desc(Year), Authors) |>
  select(Authors, Year, titlelink, Publisher) |>
  gt() |>
    fmt_markdown(columns = titlelink) |>
    tab_options(table.font.size = px(12)) |>
    cols_label(titlelink = "Title") |> 
    cols_width(
      Authors ~ pct(40),
      Year ~ pct(10),
      titlelink ~ pct(40),
      Publisher ~ pct(10)) |>
  cols_align("left") |>
  tab_style(
    style = cell_text(weight = "bold", style = "italic", color = "#BE3838"),
    locations = cells_column_labels(everything())
  )
```


# BOOK CHAPTERS

```{r}
#| echo: false
#| message: false
library(readr)
library(dplyr)
library(tidyr)
library(gt)
library(glue)
library(lubridate)
pubs <- read_csv("chapters.csv")
pubs |>
  mutate(titlelink = ifelse(is.na(Webpage), Title, glue("[{Title}]({Webpage})"))) |>
  arrange(desc(Year), Authors) |>
  select(Authors, Year, titlelink, Pages, Book, Editors, Publisher) |>
  gt() |>
    fmt_markdown(columns = titlelink) |>
    tab_options(table.font.size = px(12)) |>
    cols_label(titlelink = "Title") |> 
    cols_width(
      Authors ~ pct(25),
      Year ~ pct(5),
      titlelink ~ pct(25),
      Pages ~ pct(5),
      Book ~ pct(20),
      Editors ~ pct(20),
      Publisher ~ pct(5)) |>
  cols_align("left") |>
  tab_style(
    style = cell_text(weight = "bold", style = "italic", color = "#BE3838"),
    locations = cells_column_labels(everything())
  )
```


# SCIENTIFIC JOURNALS

```{r}
#| echo: false
#| message: false
library(readr)
library(dplyr)
library(tidyr)
library(gt)
library(glue)
library(lubridate)
pubs <- read_csv("journals.csv", locale = locale(encoding = "Windows-1252"))
pubs |>
  mutate(Webpage = ifelse(is.na(DOI),NA,paste0("https://dx.doi.org/",DOI))) |>
  mutate(titlelink = ifelse(is.na(Webpage), Title, glue("[{Title}]({Webpage})"))) |>
  mutate(temp = ifelse(is.na(Vol),Journal,paste(Journal,Vol,sep=", ")),
         Journal = ifelse(is.na(pages), temp, paste(temp,pages,sep=", "))) |>
  arrange(desc(Year), Authors) |>
  select(Authors, Year, titlelink, Journal) |>
  gt() |>
    fmt_markdown(columns = titlelink) |>
    tab_options(table.font.size = px(12)) |>
    cols_label(titlelink = "Title") |> 
    cols_width(
      Authors ~ pct(35),
      Year ~ pct(5),
      titlelink ~ pct(35),
      Journal ~ pct(25)) |>
  cols_align("left") |>
  tab_style(
    style = cell_text(weight = "bold", style = "italic", color = "#BE3838"),
    locations = cells_column_labels(everything())
  )
```

# CONFERENCE PROCEEDINGS

```{r}
#| echo: false
#| message: false
library(readr)
library(dplyr)
library(tidyr)
library(gt)
library(glue)
library(lubridate)
pubs <- read_csv("proceedings.csv")
pubs |>
  mutate(titlelink = ifelse(is.na(Webpage), Title, glue("[{Title}]({Webpage})"))) |>
  mutate(Volume = ifelse(is.na(Pages),Volume,paste(Volume,Pages,sep=","))) |>
  arrange(desc(Year), Authors) |>
  select(Authors, Year, titlelink, Editors, Volume) |>
  mutate (Editors = ifelse (is.na(Editors), "", Editors),
          Volume = ifelse (is.na(Volume), "", Volume)) |>
  gt() |>
    fmt_markdown(columns = titlelink) |>
    tab_options(table.font.size = px(12)) |>
    cols_label(titlelink = "Title") |> 
    cols_width(
      Authors ~ pct(20),
      Year ~ pct(5),
      titlelink ~ pct(25),
      Editors ~ pct(20),
      Volume ~ pct(30)) |>
  cols_align("left") |>
  tab_style(
    style = cell_text(weight = "bold", style = "italic", color = "#BE3838"),
    locations = cells_column_labels(everything())
  )
```

