---
title: "Teaching"
---

## Undergraduate

Introductory statistics

Introductory mathematical statistics

Applied multivariate statistics

Data science - supervised and unsupervised learning

Stochastic processes

---


## Postgraduate

Honours: Design of Experiments

Honours: Multivariate statistics

Honours: R programming

Masters: Multivariate statistics

Masters: Multidimensional scaling

Masters: Advanced Topics in Regression

---


## Cirriculum development

Undergraduate: Data science - big data and deep learning

Masters: Multivariate statistics

Masters: Advanced Topics in Regression

---


## PhD students

```{r}
#| echo: false
#| message: false
library(readr)
library(dplyr)
library(tidyr)
library(gt)
library(glue)
library(lubridate)
stds <- read_csv("PhDs.csv")
stds |>
  mutate(Graduated = replace_na(as.character(Graduated), "")) |>
  arrange(Graduated != "", desc(Graduated), Student) |>
  select(Student, Degree, Role, `Thesis Title`, Graduated) |>
  gt() |>
    gt::cols_width(
      Student ~ px(200),
      Degree ~ px(80),
      Role ~ px(100),
      `Thesis Title` ~ px(200),
      Graduated ~ px(50)) |>
  cols_align("left") |>
  cols_align(align = "right", columns = Graduated) |>
  tab_style(
    style = cell_text(weight = "bold", style = "italic", color = "#BE3838"),
    locations = cells_column_labels(everything())
  )
```

## Masters students

```{r}
#| echo: false
#| message: false
library(readr)
library(dplyr)
library(tidyr)
library(gt)
library(glue)
library(lubridate)
stds <- read_csv("Masters.csv")
stds |>
  mutate(Graduated = replace_na(as.character(Graduated), "")) |>
  arrange(Graduated != "", desc(Graduated), Student) |>
  select(Student, Degree, Role, `Thesis Title`, Graduated) |>
  gt() |>
    gt::cols_width(
      Student ~ px(200),
      Degree ~ px(80),
      Role ~ px(100),
      `Thesis Title` ~ px(200),
      Graduated ~ px(50)) |>
  cols_align("left") |>
  cols_align(align = "right", columns = Graduated) |>
  tab_style(
    style = cell_text(weight = "bold", style = "italic", color = "#BE3838"),
    locations = cells_column_labels(everything())
  )
```


